Tobacco

### 2024-10-23 docsrc/documentation/notebooks/loneliness.Rmd

---
title: "Loneliness"
output: html_document
bibliography: 
  - "refs.bib"  # bib reference depending on where the file is being run. Use this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging. Make sure to switch back when done..
---

# Loneliness

Introductory fluff. Why do we need this module? test reference [@1987:nelson].

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

## Methods

@@

## Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/loneliness_clm_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

## References

>>>>

---
title: "Loneliness"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`" # finally figure out how to combine these for debugging and actual 
---

## Loneliness

```{r setup, include=FALSE}
library(here)
library(glmnet)
library(plyr)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "loneliness", "rfo", "loneliness_RFO.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$loneliness
data$loneliness_last <- data$loneliness

preds <- ranger::predictions(stats::predict(model, data))
column_names <- colnames(preds)
preds <-glmnet::rmult(preds)
preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
v <- "loneliness"

```

### Methods

@@

```{r loneliness_data}
discrete_barplot(obs, 'loneliness')
```

### Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
discrete_barplot2(obs, preds, "loneliness") 
rfo_output(model)
```

### References

### 2024-10-23 docsrc/documentation/notebooks/mental_well_being.Rmd

---
title: "Mental Well-Being"
output: html_document
bibliography: 
  - "docsrc/refs.bib"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir= "../minos")
```

@@

```{r load_data, include=FALSE}
source("docsrc/documentation/notebooks/sphinx_notebook_utils.R")
```

@@

```{r SF12_Density}
continuous_density("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")  
```

@@

```{r SF12_Output, echo=FALSE}
options(width=120)
ols_output("data/transitions/SF_12/OLS/SF_12_2018_2019.rds")
ols_histogram("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")
```

>>>>

---
title: "Mental Well-Being"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"
---

@@

```{r load_data, include=FALSE}
library(here)
source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "SF_12", "lmm", "SF_12_LMM.rds")
model <- readRDS(model_path)

obs <- model@frame$SF_12
preds <- predict(model, type='response')
v <- "SF_12"
```

@@

@@

```{r SF12_Output, echo=FALSE}
options(width=120)
#ols_output("data/transitions/SF_12/OLS/SF_12_2018_2019.rds")
#ols_histogram("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")

#glmm_output(model_path)
continuous_densities(obs, preds, v)
print(summary(model))
plot(model)
```

### 2024-10-23 docsrc/documentation/notebooks/tobacco.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

---
title: "Tobacco"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

@@

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

@@

```{r tobacco_data}
counts_density('ncigs')
```

@@

```{r tobacco_output, echo=FALSE}
options(width=120)
zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
zip_density("../../../data/transitions/test/tobacco_zip_2018_2019.rds", 'ncigs_next')
```

>>>>

---
title: "Tobacco"
output:
  pdf_document: default
  html_document: default
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"
---

```{r setup, include=FALSE}
library(here)
library(glmnet)
library(plyr)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "ncigs", "rfo", "ncigs_RFO.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$ncigs
data$ncigs_last <- data$ncigs

preds <- ranger::predictions(stats::predict(model, data))
column_names <- colnames(preds)
preds <-glmnet::rmult(preds) - 1
preds <- 5 * preds

v <- "ncigs"

```

@@

@@

```{r tobacco_data}
discrete_barplot(obs, "ncigs")
```

@@

```{r tobacco_output, echo=FALSE}
options(width=120)
discrete_barplot2(obs, preds, "housing_quality") 
rfo_output(model)
```
